---
title: "SRA - RNA seq analysis"
auther: ""
output:
  html_document:
    highlight: pygments
    css: vscode.css
    toc: true
    toc_float: true
    toc_depth: 3
    number_section: true
    fig_caption: true
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, cache = TRUE, fig.align = 'center')
```

# 启动


```{r,message=FALSE}
library(SRAdb)
```

# 下载SRA元文件

打开一个SRA项目主页，右上角$Send to \rightarrow File \rightarrow RunInfo \rightarrow Create File$。

# 下载SRA文件

可以用R口命又 白纟纟日 日日 王目 土工wycrxgjgfal。王但是文件通常很大，以下言法有可能会中断或立卡纟死。
```{r message = FALSE}
sri<-read.csv("../data/SraRunInfo.csv", stringsAsFactors = FALSE)
files<-basename(sri$download_path)
for(i in 1:length(files)) download.file(sri$download_path[i], paste0('../data/', files[i]))
```

```{r}
stopifnot( all(file.exists(files)) ) 
for(f in files) {
  cmd = paste("fastq-dump --split-3", f)
  cat(cmd,"\n")#print the current command
  system(cmd) # invoke command
}
```


# References

貌似这个标题只能用英文。如果有参考文献，请删除这段说明文字，只留下一个标题。开头yaml段落的`bibliography`指向引文bib文件。如果没有引文，则须删除`bibliography`字段。

If any biblography is specified, please delet this note, and only reserve the Reference header, which should remain exactly the current character. If no biblography is specified, please delet the `biblography` in the yaml.
